### 2015-05-13 evaluation.tex
update in evaluation text

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was given a time budget of 10 hours (T.O. denotes timeout), and we considered context-switch bounds (csb) of 2, 5 and 9, respectively. When we run standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{corral}).

We can notice that \whoop is significantly faster than \corral. This is expected as \whoop achieves scalability using over-approximation. For example, \corral timeouts in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze r8169 in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some of its entry points, which might get \corral stuck.

>>>>

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a context-switch bound (csb) of 2, 5 and 9, respectively. For standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral timeouts in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization.

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in the majority of the cases. We noticed speedups between 1.5--20x.
